\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 pwarel.tex
.

\subsection{PWA Relational Abstraction}

Given an abstraction, we can define its enrichment

We now briefly overview the approach, which consists of three
steps

Discover the abstraction 
enriches the abstraction
formulates a BMC query
concretizes

@@

\subsection{Graph Abstraction}
DEFINITION 3.4 (ABSTRACT STATE GRAPH). Let ∆ > 0 be
a fixed time step. The abstract state graph H(∆) for time step ∆
is defined by the set of vertices C, and edges (Ci, Cj ) whenever
Ci
∆ Cj . Let C0 denote the collection of initial cells in C, i.e., cells
Ci such that Ci ∩ X0 6= ∅. Further, let Cu denote the set of unsafe
cells, or cells Cj such that there is a state xj ∈ Cj that reaches
an unsafe state y ∈ Xf within time 0 ≤ tj < ∆. The abstraction
H(∆) is given by D
C,
∆ , C0, Cu
E
.

\subsection{Enriched Graph Abstraction}

>>>>

A discrete abstraction over a continuous space uses relations to
describe the behavior of the system over time. Such relations abstract
the underlying relation between concrete states, and concrete paths
can no longer be constructed directly. Instead, search procedueres
like Counter-Example Guided Refinement must be used to find concrete
paths. In general, search techniques are exponential with respect to
computational resources and memory. As an alternative, we introduce
data driven `enrichment' of abstractions to approximate the concrete
relations underlying the abstract relations. Informally, we use linear
regression to compute affine maps associated with the relations
between two abstract states. We then show how associating the computed
maps with the relations transforms a discrete abstraction into a PWA
transitions system.

@@

\subsection{Graph Abstraction}
The abstraction of the hybrid dynamical system is defined by
paritioning the combiend state-input space $\HybridStates \times
\Inputs$ into hyper-rectangles or cells $C_i \in \C$. The cells are
pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
their union $\bigcup_{C_i\in\C}C_i$ is the state-input
space $\HybridStates \times \Inputs$. This discrete abstraction over
the continuous space is implicit and defined using a quantization
function $Q_d$ parameterized by the precision $d$.
This further
defines an equivalence relations such that
\[
    (\vx_i, \vu_i) \equiv (\vx_j, \vu_j) \;\text{iff}\; Q()
\]

$(\vx_i, \vu_i) \in C_i \; \text{iff} \; \C_i = Q(\vx_i, \vu_i)$

\begin{definition}[] Let C be a d-quantized tiling. The d-quantized
    tiling-based plant abstraction (denoted Pd) is given by a graph
    (V, E), where V = C, and the set of edges E is defined such that
    (Cj, Ck) ∈ E iff: there is a state-input pair (x, u) ∈ Cj and a
state-input pair (x 0 , u) ∈ Ck such that x 0 = SIM(x, u, τ ).
\end{definition}

\begin{definition}[Abstract State Graph]. Let ∆ > 0 be a fixed time
    step. The abstract state graph H(∆) for time step ∆ is defined by
    the set of vertices C, and edges (Ci, Cj ) whenever Ci ∆ Cj . Let
    C0 denote the collection of initial cells in C, i.e., cells Ci
    such that Ci ∩ X0 6= ∅. Further, let Cu denote the set of unsafe
    cells, or cells Cj such that there is a state xj ∈ Cj that reaches
    an unsafe state y ∈ Xf within time 0 ≤ tj < ∆. The abstraction
H(∆) is given by D C, ∆ , C0, Cu E .  \end{definition}

\subsection{Enriched Abstraction}
